Designing Robust Controllers With Optimal $H_{\infty}$ Performance Using Frequency-Domain Data

### 2017-02-14 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

\title{Designing Robust Controllers With $H_{\infty}$ Performance Using Frequency-Domain Data}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, a new frequency-domain method for designing robust controllers is proposed that provides optimal $\mathcal{H}_{\infty}$ performance. A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance. A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work. 
\end{abstract}

@@

Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The problem is convexified by constructing a linearly parameterized controller and devising linear constraints with respect to a desired open-loop transfer function.  A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. However, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which is based on an initial stabilizing controller. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure.

In the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem. This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem. In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order controller (which has desirable practical implications). A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation). Additionally, it will be shown that the proposed method produces a solution that converges to the global optimal solution of the $\mathcal{H}_{\infty}$ problem under certain conditions. A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints. It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the .

This paper is organized as follows: In Section \ref{sec:pre}, the class of models, controllers and control objectives are defined. Section \ref{sec:problem_form} will address the conditions required for robust performance and the optimization methods used to obtain a solution to the $\mathcal{H}_{\infty}$ problem. Section \ref{sec:sim} will demonstrate the effectiveness of the proposed method and establish the efficacy for the convex approximation of the $\mathcal{H}_{\infty}$ criterion. Finally the concluding remarks are given in Section \ref{sec:conclusion}.

@@

\section{Preliminaries} \label{sec:pre}
\subsection{Class of Models}
The set of all linear time-invariant (LTI) single-input-signal-output (SISO) stable strictly proper models belonging to the family of perturbed plants with multiplicative uncertainty can be defined as follows:
\begin{equation}\label{eq:uncert_set}
\mathcal{G} = \{ G_p(s)[1+\Delta_p(s) W_{2_{p}}(s)]; \quad p=1,\ldots,q\}
\end{equation}  
where $G_p(s)$ is the nominal model of the process, $W_{2_{p}}(s)$ is an uncertainty weight with bounded infinity norm, and $\Delta_p(s)$ is an unknown stable transfer function satisfying $\| \Delta_p \|_{\infty}<1$. For simplicity, one model from the set $\mathcal{G}$ will be analyzed, and the subscript $p$ will be omitted.

@@

\subsection{Class of Controllers}
The controllers $X(s)$ and $Y(s)$ for this control scheme will be parameterized in the decision vector $\bm{\rho}$, and can be expressed as
\begin{equation}
\begin{aligned} \label{eq:cont}
X(\bm{\rho},s) &= \bm{\rho}_x^{\top} \bm{\phi}_x(\bm{\rho},s)\\
Y(\bm{\rho},s) &= \bm{\rho}_y^{\top} \bm{\phi}_y(\bm{\rho},s)\\
\end{aligned}
\end{equation}
where $\bm{\rho}_x \in \mathbb{R}^{n_x}$, $\bm{\rho}_y \in \mathbb{R}^{n_y}$, and $\{\bm{\phi}_x(\bm{\rho},s), \bm{\phi}_y(\bm{\rho},s)\}$ are vectors of stable transfer functions chosen from a set of orthogonal basis functions. An example of such a function is the Laguerre basis function \cite{Kar13}:
\begin{equation} \label{eq:Laguerre}
\phi_{\{x,y\}_1}(s)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_c}(s-\rho_c)^{q-2}}{(s+\rho_c)^{q-1}}
\end{equation}
for $q = 2,\ldots,n$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
\begin{equation} \label{eq:Laguerre_z}
\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_d^*(1-\rho_d z)^{q-2}}{(z-\rho_d)^{q-1}}
\end{equation}
where $\rho_d^* = \sqrt{1-\rho_d^2}$ and $\{\rho_d \in \mathbb{R}: -1 < \rho_d < 1\}$. Note that when $\rho_d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.

A PID controller can also be represented in coprime form. Suppose that the desired controller structure is given as:
\begin{equation} \label{eq:pid}
K(\bm{\rho},s)=\rho_1 + \rho_2 \frac{1}{s} + \rho_3 \frac{s}{T_fs+1}
\end{equation}
Then the coprime controllers can be expressed as follows:
\begin{equation}
\begin{aligned} \label{eq:pid_2}
X(\bm{\rho},s) &= \frac{(\rho_1 T_f+\rho_3)s^2 + (\rho_1+\rho_2 T_f)s + \rho_2}{(s+\rho_c^{\prime})^2}\\
Y(\bm{\rho},s) &= \frac{s(T_fs+1)}{(s+\rho_c^{\prime})^2}
\end{aligned}
\end{equation}
where $\rho_c^{\prime} \in \mathbb{R}_+$. With the PID, note that if $\rho_c^{\prime}$ is fixed, then the coprime $X$ is linearly parameterized while $Y$ is a TF independent of the decision variables. This will always be the case when the controller $K$ is linearly parameterized.
\section{Problem Formulation} \label{sec:problem_form}
The methods described in this paper are associated with minimizing the $\mathcal{H}_{\infty}$ norm of a desired weighted sensitivity function. The sensitivity function $S(s)$ and complementary sensitivity function $T(s)$ associated with this control scheme can be formulated as follows:
\begin{equation}
\begin{aligned} \label{eq:S}
S(s) &:= e/r =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned} \label{eq:T}
T(s) &:= y/r =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
where $L(s) = G(s)K(s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$). From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\columnwidth]{../pics/circle_rotation_RP.pdf}
\caption{Graphical interpretation of the $\mathcal{H}_\infty$ robust performance constraint in the complex plane.}
\label{fig:circle}
\end{figure}

where $\psi(\bm{\rho}) = NX(\bm{\rho})+MY(\bm{\rho})$. Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\bm{\rho})$ and has radius $\gamma^{-1}\left[ |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right]$ (as shown in Fig.~\ref{fig:circle}). The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. In \cite{KNZ16}, the authors show that there exists a function $F(s)$ that can rotate this circle such that it lies on the right-hand side of the $j\omega$ axis of the complex plane (i.e., all values on and within the circle have positive real parts). This condition is recalled with the following Lemma:

@@

With the above Lemma, a necessary and sufficient condition can be derived for attaining robust performance. In \cite{KNZ16}, it is shown that if $X(\bm{\rho})$ and $Y(\bm{\rho})$ are linearly parameterized, then a convex optimization problem can be formulated as follows: 
\begin{equation} \label{eq:convex_con}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} \left[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right] < \Re\{\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
Notice that (\ref{eq:convex_con}) is a semi-infinite programming (SIP) optimization problem since there are a finite number of optimization variables and an infinite number of constraints. This problem can be solved by presetting a frequency grid $\omega$ and solving a finite number of constraints. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}).

\subsection{Optimal Performance via Nonlinear Programming}
In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem. However, it is impractical and sometimes impossible to implement large order controllers in a real system.

One solution to this problem is to find the optimal solution for a fixed low-order controller. According to Lemma \ref{lem1}, it is known that there exists a stable transfer function $F$ such that the constraint to the $\mathcal{H}_{\infty}$ problem is satisfied. Therefore, the optimal solution to this problem can be accomplished by fixing the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ and implementing the following optimization problem:
\begin{equation} \label{eq:opt_true}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |F(\bm{\rho})|\big[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \big] \\ &&& \hspace{3.3cm}<   \Re\{F(\bm{\rho})\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
where $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
\begin{equation} \label{eq:Laguerre_sum_c}
F(\bm{\rho}) = \rho_{f_{1}}+ \sum_{p=2}^{q} \rho_{f_{p}}\frac{\sqrt{2 \rho_o}(s-\rho_o)^{p-2}}{(s+\rho_o)^{p-1}}
\end{equation}
where $\rho_o \in \mathbb{R}_+$. It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases. The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.

@@

By using the relations in (\ref{eq:the_eq_1}) and (\ref{eq:the_eq_2}), one can compute $|\gamma_o - \gamma_n^*|$ as follows:
\begin{equation}
\begin{split}
|\gamma_o - \gamma_n^*|  & \leq \sup_{\omega \in \Omega} \bigg| \frac{|W_1MY_oF_o| + |W_2NX_oF_o|}{|\Re \{\psi_o F_o \}|}  \\  & \hspace{2cm}- \frac{|W_1MY_oF_n^*| + |W_2NX_oF_n^*|}{| \Re \{\psi_o F_n^* \}|} \bigg|
\end{split}
\end{equation}
However, according to \cite{AN99b}, it is known that
\begin{equation}
\lim_{n \to \infty} \|F_o - F_n^* \|_{\infty} = 0
\end{equation}
From this relation, it can be deduced that $\lim_{n \to \infty} |F_n^*| \rightarrow |F_o|$ and $\lim_{n \to \infty} \Re \{F_n^*\} \rightarrow \Re\{F_o\}$. Therefore, we obtain the following result:
\begin{equation}
\lim_{n \to \infty} |\gamma_o - \gamma_n^*|  = 0
\end{equation}
However, $\gamma_n$ (the solution to the optimization problem in (\ref{eq:opt_true})) is always less than or equal to $\gamma_n^*$ and greater that the optimal solution $\gamma_o$ if the structures of $X$ and $Y$ are the same as $X_o$ and $Y_o$, respectively. Therefore, $\gamma_n$ converges from above to $\gamma_o$, and this convergence is monotonic because the basis functions $F_n$ of order $n$ are a subset of those of order $n+1$, which ensures that $\gamma_{n+1} \leq \gamma_n$.
{\hfill \ensuremath{\blacksquare}}

@@

\subsection{Example 1: Convergence to Optimal Solution}
Consider the following discrete time SISO system:
\begin{equation}
G(z) = \frac{z-0.186}{z^3 - 1.116z^2 + 0.465z-0.093}
\end{equation}
Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$. 
\begin{remark*}
Discrete-time systems can also be considered since the proposed method uses the FRF of a system for the controller synthesis. The FRF between continuous-time and discrete-time systems are nearly identical when the Shannon sampling condition is met.
\end{remark*}
The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
\begin{equation}
W_1(z) = \frac{0.4902(z^2-1.0431z+0.3263)}{(z-1)(z-0.282)}
\end{equation}
For this controller synthesis, we can simply select the basis functions in (\ref{eq:Laguerre_z}) to be FIR filters (i.e., $\rho_d = 0$) for $X(\bm{\rho})$ and $Y(\bm{\rho})$. In order to avoid unboundedness of $W_1$ at $\omega = 0$ and have integral action, the basis functions for $Y(\bm{\rho})$ will be multiplied by $(z-1)/z$. It will be shown that as the order of $F(\bm{\rho})$ increases, the optimal solution $\gamma$ will decrease monotonically and converge to the optimal solution.

\subsubsection{Simulation Results}
The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a fifth-order controller. Therefore, according to Theorem.\ref{thm_1}, a fifth-order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution). Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.  Let $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given $n_f$-th order of $F(\bm{\rho})$. Figure.~\ref{fig:ex1_1} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases. Additionally, when the parameter $\rho_d$ is a decision variable, the convergence time is reduced.

>>>>

\title{Designing Robust Controllers With Optimal $H_{\infty}$ Performance Using Frequency-Domain Data}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, a new frequency-domain method for designing robust controllers is proposed that provides optimal $\mathcal{H}_{\infty}$ performance. A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance. It is shown that the optimal solution to the $\mathcal{H}_\infty$ problem is attained for a fixed-structure controller without any conservatism. A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work. 
\end{abstract}

@@

Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The problem is convexified by constructing a linearly parameterized controller and devising linear constraints with respect to a desired open-loop transfer function.  A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. However, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which is based on an initial stabilizing controller. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure. More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}. These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point.

In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem. This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem. In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order fully-parameterized controller (which has desirable practical implications). A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation). Additionally, it will be shown that the proposed method produces a solution that converges to the global optimal solution of the $\mathcal{H}_{\infty}$ problem under certain conditions. A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints. It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the results.

This paper is organized as follows: In section \ref{sec:pre}, the class of models and controllers are defined. Section \ref{sec:problem_form} will address the control objectives and the conditions required for robust performance; an optimization problem will be formulated to obtain a solution to the $\mathcal{H}_{\infty}$ problem. Section \ref{sec:sim} will demonstrate the effectiveness of the proposed method and establish the efficacy for the convex approximation of the $\mathcal{H}_{\infty}$ criterion. Finally the concluding remarks are given in Section \ref{sec:conclusion}.

@@

\section{Preliminaries} \label{sec:pre}
\subsection{Class of Models}
The set of all linear time-invariant (LTI) single-input-signal-output (SISO) strictly proper models belonging to the family of perturbed plants with multiplicative uncertainty can be defined as follows:
\begin{equation}\label{eq:uncert_set}
\mathcal{G} = \{ G_p(s)[1+\Delta_p(s) W_{2_{p}}(s)]; \quad p=1,\ldots,q\}
\end{equation}  
where $G_p(s)$ is the nominal model of the process, $W_{2_{p}}(s)$ is an uncertainty weight with bounded infinity norm, and $\Delta_p(s)$ is an unknown stable transfer function satisfying $\| \Delta_p \|_{\infty}<1$. For simplicity, one model from the set $\mathcal{G}$ will be analyzed, and the subscript $p$ will be omitted.

@@

\subsection{Class of Controllers}
The controllers $X(s)$ and $Y(s)$ for this control scheme will be parameterized in the decision vector $\bm{\rho}$, and can be expressed as
\begin{equation}
\begin{aligned} \label{eq:cont}
X(\bm{\rho},s) &= \bm{\rho}_x^{\top} \bm{\phi}_x(\bm{\rho},s)\\
Y(\bm{\rho},s) &= \bm{\rho}_y^{\top} \bm{\phi}_y(\bm{\rho},s)\\
\end{aligned}
\end{equation}
where $\bm{\rho}_x \in \mathbb{R}^{n_x}$, $\bm{\rho}_y \in \mathbb{R}^{n_y}$, and $\{\bm{\phi}_x(\bm{\rho},s), \bm{\phi}_y(\bm{\rho},s)\}$ are vectors of stable transfer functions chosen from a set of orthogonal basis functions. An example of such a function is the Laguerre basis function \cite{Kar13}:
\begin{equation} \label{eq:Laguerre}
\phi_{\{x,y\}_1}(s)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_c}(s-\rho_c)^{q-2}}{(s+\rho_c)^{q-1}}
\end{equation}
for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
\begin{equation} \label{eq:Laguerre_z}
\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_d^*(1-\rho_d z)^{q-2}}{(z-\rho_d)^{q-1}}
\end{equation}
where $\rho_d^* = \sqrt{1-\rho_d^2}$ and $\{\rho_d \in \mathbb{R}: -1 < \rho_d < 1\}$. Note that when $\rho_d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.

A PID controller can also be represented in coprime form. Suppose that the desired controller structure is given as:
\begin{equation} \label{eq:pid}
K(\bm{\rho},s)=\rho_1 + \rho_2 \frac{1}{s} + \rho_3 \frac{s}{T_fs+1}
\end{equation}
Then the coprime controllers can be expressed as follows:
\begin{equation}
\begin{aligned} \label{eq:pid_2}
X(\bm{\rho},s) &= \frac{(\rho_1 T_f+\rho_3)s^2 + (\rho_1+\rho_2 T_f)s + \rho_2}{(s+\rho_c^{\prime})^2}\\
Y(\bm{\rho},s) &= \frac{s(T_fs+1)}{(s+\rho_c^{\prime})^2}
\end{aligned}
\end{equation}
where $\rho_c^{\prime} \in \mathbb{R}_+$. With the PID, note that if $\rho_c^{\prime}$ is fixed, then the coprime $X$ is linearly parameterized while $Y$ is a TF independent of the decision variables. This will always be the case when the controller $K$ is linearly parameterized.
\section{Problem Formulation} \label{sec:problem_form}
The methods described in this paper are associated with minimizing the $\mathcal{H}_{\infty}$ norm of a desired weighted sensitivity function. The sensitivity function $S(s)$ and complementary sensitivity function $T(s)$ associated with this control scheme can be formulated as follows:
\begin{equation}
\begin{aligned} \label{eq:S}
S(s) &:= e/r =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned} \label{eq:T}
T(s) &:= y/r =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$). From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\columnwidth]{../pics/circle_rotation_RP.pdf}
\caption{Graphical interpretation of the $\mathcal{H}_\infty$ robust performance constraint in the complex plane.}
\label{fig:circle}
\end{figure}
where $\psi(\bm{\rho}) = NX(\bm{\rho})+MY(\bm{\rho})$. Consider a circle in the complex plane at a specific frequency in $\Omega$ which is centered at $\psi(\bm{\rho})$ and has radius $\gamma^{-1}\left[ |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right]$ (as shown in Fig.~\ref{fig:circle}). The constraint in (\ref{eq:circle}) ensures that for any frequency point in $\Omega$, the circle associated with this frequency point will not encircle the origin. In \cite{KNZ16}, the authors show that there exists a function $F(s)$ that can rotate this circle such that it lies on the right-hand side of the $j\omega$ axis of the complex plane (i.e., all values on and within the circle have positive real parts). This condition is recalled with the following Lemma:

@@

With the above Lemma, a necessary and sufficient condition can be derived for attaining robust performance. In \cite{KNZ16}, it is shown that if $X(\bm{\rho})$ and $Y(\bm{\rho})$ are linearly parameterized, then a convex optimization problem can be formulated as follows: 
\begin{equation} \label{eq:convex_con}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} \left[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \right] < \Re\{\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
Notice that (\ref{eq:convex_con}) is a semi-infinite programming (SIP) optimization problem since there are a finite number of optimization variables and an infinite number of constraints. This problem can be solved by presetting a frequency grid $\omega$ and solving a finite number of constraints. This frequency grid can be predefined in a variety of manners (see \cite{SVBB11}, \cite{GKL10b}, and \cite{FR05}).

\subsection{Optimal $\mathcal{H}_{\infty}$ Performance}
In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem. However, it is impractical and sometimes impossible to implement large order controllers in a real system.

One solution to this problem is to find the optimal solution for a fixed low-order controller. According to Lemma \ref{lem1}, it is known that there exists a stable transfer function $F$ such that the constraint to the $\mathcal{H}_{\infty}$ problem is satisfied. Therefore, the optimal solution to this problem can be accomplished by fixing the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ and implementing the following optimization problem:
\begin{equation} \label{eq:opt_true}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |F(\bm{\rho})|\big[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \big] \\ &&& \hspace{3.3cm}<   \Re\{F(\bm{\rho})\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
where $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
\begin{equation} \label{eq:Laguerre_sum_c}
F(\bm{\rho}) = \rho_{f_{1}}+ \sum_{p=2}^{q} \rho_{f_{p}}\frac{\sqrt{2 \rho_o}(s-\rho_o)^{p-2}}{(s+\rho_o)^{p-1}}
\end{equation}
where $\rho_o \in \mathbb{R}_+$. It should be noted that the optimal solution to the $\mathcal{H}_\infty$ problem is achieved when $K(\bm{\rho}) = X(\bm{\rho})Y^{-1}(\bm{\rho})$ has the same structure as the optimal controller. However, if the structure of the optimal controller is unknown a priori, then one can simply fix the order of the basis $F(\bm{\rho})$ and vary the orders of the controllers $X(\bm{\rho})$ and $Y(\bm{\rho})$ until $\gamma$ converges to a constant value. The concept of this method will be shown in one of the examples in section \ref{sec:sim}.

It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges monotonically to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases. The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.

@@

By using the relations in (\ref{eq:the_eq_1}) and (\ref{eq:the_eq_2}), one can compute $|\gamma_o - \gamma_n^*|$ as follows:
\begin{equation}
\begin{split}
|\gamma_o - \gamma_n^*|  & \leq \sup_{\omega \in \Omega} \bigg| \frac{|W_1MY_oF_o| + |W_2NX_oF_o|}{|\Re \{\psi_o F_o \}|}  \\  & \hspace{2cm}- \frac{|W_1MY_oF_n^*| + |W_2NX_oF_n^*|}{| \Re \{\psi_o F_n^* \}|} \bigg|
\end{split}
\end{equation}
However, according to \cite{AN99b}, it is known that
\begin{equation}
\lim_{n \to \infty} \|F_o - F_n^* \|_{\infty} = 0
\end{equation}
From this relation, it can be deduced that $\lim_{n \to \infty} |F_n^*| \rightarrow |F_o|$ and $\lim_{n \to \infty} \Re \{F_n^*\} \rightarrow \Re\{F_o\}$. Therefore, we obtain the following result:
\begin{equation}
\lim_{n \to \infty} |\gamma_o - \gamma_n^*|  = 0
\end{equation}
However, $\gamma_n$ (the solution to the optimization problem in (\ref{eq:opt_true})) is always less than or equal to $\gamma_n^*$ and greater that the optimal solution $\gamma_o$ if the structures of $X$ and $Y$ are the same as $X_o$ and $Y_o$, respectively (which is the case, as postulated in the Theorem). Therefore, $\gamma_n$ converges from above to $\gamma_o$, and this convergence is monotonic because the basis functions $F_n$ of order $n$ are a subset of those of order $n+1$, which ensures that $\gamma_{n+1} \leq \gamma_n$.
{\hfill \ensuremath{\blacksquare}}

@@

\subsection{Example 1: Convergence to Optimal Solution}
Consider the following discrete time SISO system (with a sampling time of $T_s = 1s$):
\begin{equation}
G(z) = \frac{z-0.186}{z^3 - 1.116z^2 + 0.465z-0.093}
\end{equation}
Note that since this system is stable, then the coprimes can be selected as $N(z) = G(z)$ and $M(z) = 1$. 
\begin{remark*}
Discrete-time systems can also be considered since the proposed method uses the FRF of a system for the controller synthesis. The FRF between continuous-time and discrete-time systems are nearly identical when the Shannon sampling condition is met.
\end{remark*}
The control objective of this case study is to design a controller (with integral action) that minimizes the nominal performance condition $\|W_1S \|_{\infty}$ (i.e., minimize $\gamma$ in $\|W_1S \|_{\infty} < \gamma$), where
\begin{equation}
W_1(z) = \frac{0.4902(z^2-1.0431z+0.3263)}{(z-1)(z-0.282)}
\end{equation}
For this controller synthesis, we can simply select the basis functions in (\ref{eq:Laguerre_z}) to be FIR filters (i.e., $\rho_d = 0$) for $X(\bm{\rho})$ and $Y(\bm{\rho})$. In order to avoid unboundedness of $W_1$ at $\omega = 0$ and have integral action, the basis functions for $Y(\bm{\rho})$ will be multiplied by $(z-1)/z$. It will be shown that as the order of $F(\bm{\rho})$ increases, the optimal solution $\gamma$ will decrease monotonically and converge to the optimal solution.

\subsubsection{Simulation Results}
The \texttt{mixsyn} command from \texttt{MATLAB}'s Robust Control toolbox yields an optimal value of $\gamma^* = 0.5522$ with a 5\textsuperscript{th} order controller. Therefore, according to Theorem.\ref{thm_1}, a 5\textsuperscript{th} order controller was also implemented with the proposed method (i.e., to ensure convergence to the optimal solution). Additionally, two simulations were performed with the proposed method; one simulation with $F(\bm{\rho})$ selected such that the basis function is an FIR filter (i.e., Laguerre basis functions in (\ref{eq:Laguerre_z}) with $\rho_d = 0$) and one simulation with $F(\bm{\rho})$ selected such that $\rho_d$ is a decision variable.  Let $\gamma_{n_f}$ denote the optimal solution of the nominal performance condition for a given $n_f$-th order of $F(\bm{\rho})$. Figure.~\ref{fig:ex1_1} shows the convergence of the optimal solution $\gamma_{n_f}$ as a function $n_f$; it can be observed that with the proposed frequency-domain method, the optimal solution to the $\mathcal{H}_{\infty}$ problem converges monotonically as the order of $F(\bm{\rho})$ increases. Additionally, when the parameter $\rho_d$ is a decision variable, the convergence time is reduced.
